%chapter 1

\chapter{Introduction} % Write in your own chapter title
\label{Chapter0}
\lhead{Chapter 0. \emph{Introduction}} % Write in your own chapter title to set the page header

\section{Motivation}
The main objective or motivation of this report is to increase the knowledge about the concepts of Power Electronics. To practically apply all the concepts and prove them. This project is simulations based and is being done on Simulink ,Matlab. In this we have Simulated the three type of circuits which covers most of the power electronics course and have matched the simulated results with the theoretical ones. The building blocks of the project are rectifier ,inverter and LCL filter. The industrial application of this in the ups in which AC is first converted into DC which is used for charging the batteries and the output of batteries which is DC voltage is then converted into AC through inverters. 

\section{Problem Statment}
The problem given in the statement is to first input the three phase AC source whose magnitude is to be 400V. The three phases are displaced by 120 degrees as in case of practical ones. Then the input is to be passed through rectifier which converts it into DC. The Rectifier we have used in this case in controlled rectifier whose firing angle  can be adjusted such that we can vary the the output voltage. The gate pulses are used for controlling the firing angle .The gate pulses are such that no thristors of same leg will be on at the time instant  .The output voltage is 400Vdc. This DC voltage is then fed into the inverter circuit. The inverter being used is three phase sine-pwm. The inverter converts the dc voltage into three phase AC. The three phase AC is such that it contains the steps. The three steps are then converted into the sine waveform using the LCL filter. The filter is designed such that the output voltage is pure sine waveform.    
